---
title: "Practical Machine Learning"
author: "Hao YU"
date: "December 18, 2015"
output: html_document
---


Load the data on my desktop, and remove the X variable.
```{r}
pml.training <- read.csv("~/Desktop/pml-training.csv")
pml.testing <- read.csv("~/Desktop/pml-testing.csv")

pml.training<-pml.training[-1]
pml.testing<-pml.testing[-1]

```

Load the packages with required packages.
```{r}
library(caret)
library(FSelector)
library(randomForest)

```

Set the seed and do the in-sample partition of the training set.
```{r}
set.seed(24)
training <- createDataPartition(y=pml.training$classe, p=0.6, list=FALSE)
set.training <- pml.training[training, ]
set.testing <- pml.training[-training, ]
```

Assign blank cells to NA and remove columns with missing raito larger than 0.5.
```{r}
set.training[set.training==""]<-NA
na.factor<-c()
for(i in 1:length(set.training)) { 
  if(sum(is.na( set.training[, i])) / nrow(set.training) > 0.5 ) { 
    na.factor<-c(na.factor,i)
  }   
    } 
na.variables<-colnames(set.training[na.factor])
na.factor
na.variables
set.training<-set.training[-na.factor]

dim(set.training)
```

Exclude variables with low information gain and get 50 useful indicators.
```{r}
weights<-information.gain(classe~.,set.training)
print(weights)
factor.train<-cutoff.k(weights,50)
factor.train
```

Get the formula and random forest model.
```{r}
formula.train <- as.simple.formula(factor.train, "classe")
print(formula.train)

model.train <- randomForest(formula.train, data=set.training)
```

Use the model to predict in-sample testing data and compare results with truth.
```{r}
prediction.insample <- predict(model.train, set.testing, type = "class")

confusionMatrix(prediction.insample, set.testing$classe)
```

Adjust the levels of variables in testing data.
```{r}
levels(pml.testing$new_window)<-
  levels(set.training$new_window)

levels(pml.testing$cvtd_timestamp)<-
  levels(set.training$cvtd_timestamp)
```

Use the train model to predict the testing data and get the answers.
```{r}
answers<-predict(model.train,pml.testing,type="class")
answers

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(answers)
```

More information and reference, please visit my site: tiiome.com